\chapter{Planning \& formulation}
\newpage
\section{Planning \& formulation}

\hspace{0.6cm} Developing an SaaS platform is a tedious task. To develop a cloud storage based web application.A website which is user friendly would be the final implementation of the project. It consists of following phases:
\begin{itemize}
\item	\textbf{Phase 1: Researching about Cloud Storage:}
    Researching how to create the front end for web and also the backend databases.

\item	\textbf{Phase 2: Creating the front end for web:}
Designing the sign up and login pages and the other pages that will be accessed by users of the application. Then to make static web pages for docstash by analyzing interfaces of all other storage providers. To make web pages we started by sketching designs of web pages and then implementing it into real web pages, Also understanding way to establish back-end support.

\item	\textbf{Phase 3: Creating the backend server and linking them:}
The next step is providing strong User authentication methods. This is crucial step in cloud application or any software to ensure data integrity and confidentiality. To provide more secure access we worked on Third party user authentication. Implementing latest front and back end techniques to make application fast and dynamic.

\item	\textbf{Phase 5: Linking web application with databases:}
Implementing security features to provide more reliable platform. Providing encryption to files stored on cloud to secure it from any threat. Testing of application to find any errors or bug to deploy totally bug free platform for users.  All the steps mentioned above are merged in this final step. The most important step in this project is creating our own cloud environment, adding the data to the database, applying security methods in this critical step. 

\item	\textbf{Phase 6: Testing and deploying:}
Using a variety of inputs to test for bugs if any and correct them. Deploying the application for public use.

\end{itemize}