\chapter{Testing}
\newpage

The various testing methodologies implemented are, 

\section{Unit And Integration Testing}
The various modules of the application (Eg- Events module, Contacts module etc) were tested separately and any bugs found were fixed. After successfully finishing unit testing, all items were slowly integrated one by one wile continuously testing for compatibility testing. Finally, after all the modules were integrated, the system was again tested as a whole for proper operation.

\section{White Box Testing}
Some of the white box testing techniques used are,

\begin{itemize}
  \item [1.] Control flow analysis. The various branches of control flow were traversed atleast once.
  \item [2.] The logical decisions were evaluated.
  \item [3.] All the loops were evaluated to check their correct operation.
\end{itemize}

\section{Black Box Testing}
Some of the Black box testing techniques used are,

\begin{itemize}
  \item [1.] The menu ordering functionality was checked using boundary value analysis for all, none and few items ordered.
  \item [2.] The outputs of the various tabs were checked for correctness.
  \item [3.] Login and register functionalities were tested for correct operation.
  \item [4.] In the register functionality, the bounds on the length of username and passwords were tested.
  \item [5.] The mechanism for adding and editing items in the web application was tested for each area of function.

\end{itemize}

\section{Usability Testing}
The user interface of the application as well as the web app were tested for ease of use. Ambigous and unsuitable elements were replaced. It was verified that the application was simple and easy to use for both the residents and the administrators.

\section{Alpha and Beta Testing}
The user interface of the application as well as the web app were tested for ease of use. Ambiguous and unsuitable elements were replaced. End users were allowed to operate the application both under supervision and unsupervised. Their opinions were taken into consideration and required changes made. 
